In order to structure the evaluation we created the following testplan.

\subsection{Testplan}
Our tests are formative as our goal is to improve Amazon. \\
\textbf{Purpose:} We want to test the user's experience and satisfaction of Amazon, both pragmatically and hedonically. \\
\textbf{Main questions:}
\begin{itemize}
\item Are there parts of the system the user is not satisfied with?
\item Which parts of the system did the user not use?
\item Was there a part of the system that was troublesome to the user?
\end{itemize}
\textbf{User profile:}
\begin{itemize}
\item Ordinary Danes without a technical background.
\end{itemize}
\textbf{Participants and roles:}
\begin{itemize}
\item One of us will function as a moderator and the other will be taking notes. Also our participants are required to be capable of cooperating.
\end{itemize}
\textbf{Test methods:}
\begin{itemize}
\item Questionares : AttrakDiff
\item Lab studies : Co-discovery
\end{itemize}
\textbf{Assignments:} The assignments are generally structured as stories with the intention of making the user explore the system, without guiding the user and keeping interaction with the user minimal. Examples of the stories used can be seen in \autoref{appendix:codiscovery} \\
\textbf{Context and equipment:} In the context of the lab study we make use of the internet, a laptop for the participants, a projector to be able to observe their interaction with the system, assignments and a questionare in paper format. \\
\textbf{Data collection:} Data is collected through the questionare and notes taken during the lab study.

\subsection{Description of evaluation process}
In order to evaluate the system we combine the two methods in the following manner: \\
The two participants are present in the lab simultaneously, and are first read a loud an introduction detailing the purpose and expectations of the evaluation, this introduction can be found in \autoref{appendix:introductiontext}. 
\begin{itemize}
\item Et par af to inde samtidig
\item Oplæsning af introduktionstekst
\begin{itemize}
\item Hvordan opgaverne skal udføres
\end{itemize}
\item Blev først testet af co-discovery: moderator \& notetager
\begin{itemize}
\item Opgaver: Stories
\item ~17 minutter i alt
\end{itemize}
\item Dern\ae st individuelt udfylde Attrakdiff spørgeskemaet
\begin{itemize}
\item ~5 minutter i alt
\item Erfaring med amazon
\end{itemize}
\item Til sidst fælles evaluering
\begin{itemize}
\item Deltagers oplevelse af systemet
\item Vores m\aa l med testen/opgaverne
\end{itemize}
\end{itemize}